TMR: Detecting Structure in Graphical Data

### 2021-04-01 final-report/final-report.tex
Scaffold final report
Slight report work
Change plotting function and generalise graph init

%bibliography
\usepackage[backend=bibtex]{biblatex}
\addbibresource{interim-sources.bib}

@@

>>>>

%bibliography
\usepackage[backend=bibtex]{biblatex}
\addbibresource{final-sources.bib}

@@

\section{Bayesian Exploration}

For our inference goals we wish to sample block memberships $b$ according to the posterior $p(b | \Gcal)$. Peixoto \cite{Peixoto-MCMC} proposes a Monte-Carlo method for generating these samples. We simply

At each iteration of the Markov chain we can use the most recent block assignments to train the classifier, mapping from vertex features to detected membership. The classifier has parameters $\theta$. We wish to apply Bayesian techniques such that we retain a measurement of the uncertainty in the classification. We propose to use Stochastic Gradient Langevin Dynamics (SGLD) as described by Nemeth and Fearnhead \cite{Nemeth-SGMCMC}. This allows us to draw samples from an arbitrary distribution $\pi$ on $\theta$. We can write $\pi$ in the following form.
%
\begin{equation}
	\pi(\theta) \propto \exp \left( - U(\theta) \right)
\end{equation}

We wish to draw samples from, the posterior.
%
\begin{equation}
	p(\theta | b) = \frac{p(\theta) p(b | \theta)}{p(b)}
\end{equation}

We can generate these samples and then use them to approximate the true posterior:
%
\begin{equation}
	p(b_v = j | \Gcal) \approx \frac{1}{N} \sum_{n=1}^{N} \one \left\{ b_v^{(n)} = j \right\}
\end{equation}
